\documentclass[letterpaper,11pt]{article}

\usepackage{amsmath}
\usepackage{fullpage}
\usepackage[pdftex]{hyperref}
\usepackage{etaremune}
\usepackage{xcolor}
\usepackage[backend=biber, sorting=ydnt, style=ieee]{biblatex}
\addbibresource{papers.bib}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=mygreylink
}
\urlstyle{same}
\definecolor{mygrey}{gray}{0.75}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\newcounter{entrycount}
\AtDataInput{\stepcounter{entrycount}}
\DeclareFieldFormat{labelnumber}{\mkrevbibnum{#1}}
\newcommand{\mkrevbibnum}[1]{\number\numexpr\value{entrycount}+1-#1}

\begin{document}

\thispagestyle{empty}
\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\href{}{\LARGE Matt Reichenbach}} & \url{https://mpreichenbach.github.io} \\
%    \texttt{(303) 502-6191} \\
    \texttt{matthew.[lastname](at)gmail\_dot\_com} \\
	\end{tabular*}
\\
\vspace{0.1in}}

\mywebheader

\resheading{Research Interests}
\begin{itemize}
	\resitem{\textbf{General:} Combining mathematical and computational tools to solve challenging, real-world problems.}
	
	\resitem{\textbf{Scientific:} Machine learning, remote sensing, ecological modeling, and data science.}
	
	\resitem{\textbf{Mathematical:} Applied functional analysis, mathematical modeling, numerical analysis, optimization, and dynamical systems.}
\end{itemize}

\resheading{Education}
	\begin{itemize}
		\item
			\ressubheading{University of Nebraska-Lincoln}{Lincoln, NE}{Ph.D. in Mathematics}{Dec. 2020}
				{ \footnotesize
				\begin{itemize}
					\resitem{Dissertation: \emph{Spectral Properties of a Non-compact Operator in Ecology}}
					\resitem{Advised by Dr. Richard Rebarber and Dr. Brigitte Tenhumberg}
				\end{itemize}}
		\item
		    	\ressubheading{University of Nebraska-Lincoln}{Lincoln, NE}{M.S. in Mathematics}{May 2017}
		\item
			\ressubheading{University of Colorado Boulder}{Boulder, CO}{Post-Baccalaureate Teacher Licensure in Secondary Mathematics}{Dec. 2013}
		\item
			\ressubheading{University of Colorado Boulder}{Boulder, CO}{B.A. in Mathematics}{May 2012}
			
	\end{itemize}

\resheading{Skills}
	\begin{description}
		\item[Python:] { \footnotesize Implemented convolutional neural networks using \textbf{Keras} and  the \textbf{Tensorflow} backend; generated training datasets with the \textbf{GDAL}, \textbf{NumPy}, and \textbf{OpenCV}, libraries; trained various classifiers using \textbf{scikit-learn}, and processed tabular data with \textbf{pandas}. Proficient user of the \textbf{Anaconda} and \textbf{Miniconda} distributions.}\\
		
		\item[R:] { \footnotesize Processed fish telemetry data using the \textbf{tidyverse} libraries; fit hidden Markov models for fish behavior using \textbf{momentuHMM}, \textbf{moveHMM}, and \textbf{crawl}; interpolated spatial data using \textbf{automap}.}
		
		\item[Additional Languages:] {\footnotesize MATLAB, \LaTeX.}
		
		\item[Applications:]{\footnotesize Git, QGIS, ArcGIS, the Microsoft Office suite, Google Docs.}
		
		\item[Operating Systems:] {\footnotesize Windows, Linux}.
	\end{description}

\resheading{Selected Employment}
	\begin{itemize}
		\item
		\ressubheading{University of Colorado Boulder - Dept. of Applied Mathematics}{Boulder, CO}{Assistant Teaching Professor}{Aug. 2023 to Current}
		{\footnotesize
			\begin{itemize}
				\item Courses taught include Calculus 1 for Engineers and Statistical Methods and Applications I.
			\end{itemize}
		}
		\item
		\ressubheading{US Army Corps of Engineers - Geospatial Research Laboratory}{Alexandria, VA}{Research Mathematician}{Feb. 2021 to June 2023}
		{\footnotesize
			\begin{itemize}
				\resitem{\textbf{Enhanced Terrain Processing:} Lead developer of deep-learning models which \\ perform land-cover classification of high-resolution imagery; combined satellite and UAV imagery with publicly available land-cover data to create new datasets; trained models on a multi-GPU NVIDIA DGX machine; developed a Python library to simplify dataset-creation; incorporated the trained models into user-friendly ArcGIS toolbox.}
				\resitem{\textbf{Acoustic Deterrence of Invasive Carp:} Lead developer of movement models to determine the effects of acoustic deterrents on carp behavior; incorporated sound intensity values in a pond as a novel covariate in hidden Markov models; generated a suite of data-processing tools for fish telemetry. This project is a collaboration with with scientists at USGS and USACE's Environmental Laboratory.}
			\end{itemize}
		}
	
	\newpage
	
		\item
		\ressubheading{US Army Corps of Engineers - Geospatial Research Laboratory}{Alexandria, VA}{NSF Mathematical Sciences Graduate Intern}{Jun. 2020 -- Aug. 2020}
		{\footnotesize
			\begin{itemize}
				\resitem{\textbf{Enhanced Terrain Processing:} Developed deep-learning models to remove \\ noise from synthetic-aperture radar (SAR) imagery; created synthetic datasets from publicly available imagery; acted as technical lead with minimal oversight from mentors.}
		\end{itemize}}

		\item
			{\ressubheading{University of Nebraska-Lincoln}{Lincoln, NE}{Graduate Teaching Assistant}{Aug. 2015 -- Dec. 2020}
				{ \footnotesize
				\begin{itemize}
					\resitem{Taught courses as the instructor-of-record, directed recitation \\ sessions, and tutored in the Mathematics Resource Center}
				\end{itemize}}}

        \item
			\ressubheading{Center for Science, Mathematics \& Computer Education}{Lincoln, NE}{Instructor for MATH 806T: Number Theory and Cryptography}{Jul. 2019}
				{\footnotesize
				\begin{itemize}
				    \resitem{Co-taught this Master's-level course for in-service secondary teachers}
				\end{itemize}
				}
%        		\item
%			\begin{samepage}
%			\ressubheading{\href{https://cty.jhu.edu/}{Center for Talented Youth}}{Santa Cruz, CA}{Mathematics of Money Instructor}{June 2017 -- August 2017}
%				{\footnotesize
%				\begin{itemize}
%				    \resitem{Taught this course for an international group of  middle- and high-school students.}
%				\end{itemize}
%				}
%				\end{samepage}
		\item 
		\begin{samepage}
			\ressubheading{Daewoo Elementary School}{Geoje-si, Republic of Korea}{Head Elementary English Teacher}{Feb. 2014 -- Feb. 2015}
				{\footnotesize
				\begin{itemize}
				    \resitem{Taught four English lessons daily to $1^{\text{st}}$ through $6^{\text{th}}$-grade students}
				    \resitem{Organized English-language initiatives and acted as the liaison between  English \\ teachers and school administrators}
				\end{itemize}
				}
		\end{samepage}
%        		\item
%			\ressubheading{\href{https://www.colorado.edu/cuub/}{CU Upward Bound Summer Program}}{Boulder, CO}{Geometry \& Calculus Instructor}{June 2013 -- July 2013}
%				{\footnotesize
%				\begin{itemize}
%				    \resitem{Taught these courses to Native American high-school students from reservations \\ around the United States.}
%				\end{itemize}
%				}
        		\item
			\ressubheading{Laboratory for Atmospheric and Space Physics}{Boulder, CO}{Student Procurement Assistant VI}{Mar. 2010 -- May 2013}
				{\footnotesize
				\begin{itemize}
				    \resitem{Maintained parts lists for NASA-funded projects, including instruments \\on the GOES-R, MAVEN, and TSIS satellites}
				\end{itemize}
				}
%        		\item
%			\ressubheading{\href{https://www.colorado.edu/cuub/}{CU Upward Bound Summer Program}}{Boulder, CO}{Instructional Assistant}{June 2012 -- July 2012}
%				{\footnotesize
%				\begin{itemize}
%				    \resitem{Assisted the instructor of the Geometry and Calculus courses.}
%				\end{itemize}
%				}
%        		\item
%			\ressubheading{\href{https://www.colorado.edu/cuub/}{CU Upward Bound Summer Program}}{Boulder, CO}{Instructional Assistant}{June 2010 -- July 2010}
%				{\footnotesize
%				\begin{itemize}
%				    \resitem{Assisted the instructor of the Geometry and Algebra courses.}
%				\end{itemize}
%				}
	\end{itemize}

\resheading{Publications}

\nocite{*}
\printbibliography[heading=none]

\resheading{Awards}
\begin{itemize}
	\item 
	\ressubheading{Award for Outstanding Achievement in Student Outreach}{ERDC}{Awarded for excellence in mentoring student interns}{April, 2023}
	\item
	\ressubheading{ERDC Award for Outstanding Team Effort}{ERDC}{Awarded to the Enhanced Terrain Processing team}{April, 2022}
	\item
	\ressubheading{Linda Bors Fellowship}{UNL Math Dept.}{Awarded to three graduate students annually for excellence in research}{Fall 2018}
	\item
	\ressubheading{Steven Hataaja Award}{UNL Math Dept.}{Awarded for excellent exposition by a graduate student}{Spring 2018}
	\item
	\ressubheading{Robert Noyce Teacher Scholarship}{CU Boulder Dept. of Education}{NSF-funded merit scholarship}{Spring 2013 \& Fall 2013}
	\item
	\ressubheading{Dean's List}{CU Boulder}{Awarded to students with semester GPA greater than 3.75}{Spring 2010, Sp. 2013, \& Fall 2013}
\end{itemize}

\resheading{Presentations}
\begin{etaremune}
	\item 
	\ressubheading{American Fisheries Society Annual Meeting}{Spokane, WA}{Modeling the Effects of Acoustic Signals on Invasive Carp Behavior (20 min.)}{Aug. 2022}
	\item
	\ressubheading{ERDC RD22 Conference}{Remote}{Modeling the Effects of Deterrents on Carp Behavior (20 min.)}{Apr. 2022}
	\item
	\ressubheading{Math Club, University of Nebraska-Kearney}{Remote}{``Modeling Ecological Populations" (50 min.)}{Oct. 2020}
	%		\item
	%		\ressubheading{Final Presentation (remote), Geospatial Research Laboratory}{Alexandria, VA}{``Denoising Synthetic Aperture Radar Using Convolutional Neural Networks"}{Aug. 2020}
	%		\item
	%		\ressubheading{STAMP Meeting (remote), Geospatial Research Laboratory}{Alexandria, VA}{``Integral Projection Models in Mathematical Biology" (50 min.)}{Jun. 2020}
	\item
	\ressubheading{Math Department Colloquium, Creighton University}{Omaha, NE}{``Integral Projection Models in Mathematical Biology'' (50 min.)}{Dec. 2019}
	\item
	\ressubheading{Augustana University Math Club}{Sioux Falls, SD}{``Population Models in Mathematical Biology" (50 min.)}{Nov. 2018}
	\item
	\ressubheading{Colorado Council of Teachers of Mathematics Annual Conference}{Denver, CO}{``The Impact of Inquiry-Based Teaching in Two High School Math Classrooms''}{Oct. 2013}
\end{etaremune}
	
%\resheading{Invited Seminar Presentations}
%	\begin{etaremune}
%		\item
%		\ressubheading{MathBio Seminar (remote), University of Nebraska-Lincoln}{Lincoln, NE}{``Modeling Behavioral Changes in Invasive Carp'' (50 mins)}{Mar. 2022}
%		\item
%		\ressubheading{STAMP Meeting (remote), Geospatial Research Laboratory}{Alexandria, VA}{``Modeling Behavior Changes in Invasive Carp'' (50 mins)}{Mar. 2022}
%		\item
%		\ressubheading{Math Club (remote), University of Nebraska-Kearney}{Kearney, NE}{``Modeling Ecological Populations" (50 mins)}{Oct. 2020}
%		\item
%		\ressubheading{Final Presentation (remote), Geospatial Research Laboratory}{Alexandria, VA}{``Denoising Synthetic Aperture Radar Using Convolutional Neural Networks"}{Aug. 2020}
%		\item
%		\ressubheading{STAMP Meeting (remote), Geospatial Research Laboratory}{Alexandria, VA}{``Integral Projection Models in Mathematical Biology" (50 min.)}{Jun. 2020}
%		\item
%		\ressubheading{Math Department Colloquium, Creighton University}{Omaha, NE}{``Integral Projection Models in Mathematical Biology'' (50 min.)}{Dec. 2019}
%		\item
%		\ressubheading{Augustana University Math Club}{Sioux Falls, SD}{``Population Models in Mathematical Biology" (50 min.)}{Nov. 2018}
%	\end{etaremune}

%\resheading{Graduate School Seminar Presentations (all Lincoln, NE)}
%	\begin{etaremune}
%		\item
%		\ressubheading{Graduate Student Seminar (remote)}{}{``What Can Math Say About Conspiracy Theories?" (50 min.)}{Oct. 2020}
%		\item
%		\ressubheading{Math Bio Seminar}{}{``Asymptotic Convergence to a Stable Stage Distribution" (50 min.)}{Feb. 2020}
%		\item
%		\ressubheading{Graduate Student Seminar}{}{``Conway \& Kochen's Free Will Theorem" (50 min.)}{Oct. 2019}
%		\item
%		\ressubheading{Math Bio Seminar}{}{``A Positive Eigenvalue for a New Integral Projection Model" (50 min.)}{Oct. 2019}
%		\item
%		\ressubheading{SPiDERS Graduate Seminar}{}{``Compactness Criteria in Infinite-Dimensional Spaces I, II, \& III" (50 min.)}{Feb. 2019}
%		\item
%		\ressubheading{Graduate Student Seminar}{}{``Learnability Can be Undecidable" (50 min.)}{Jan. 2019}
%		\item
%		\ressubheading{MathBio Seminar}{}{``Cannibalism \& Stunting in an IPM for Fish" (50 min.)}{Sep. 2018}
%		\item
%		\ressubheading{Graduate Student Seminar}{}{``Continuous-Time Population Models" (50 min.)}{Sep. 2017}
%		\item
%		\ressubheading{Graduate Student Seminar}{}{``An Exploration of the Calculus of Variations" (50 min.)}{Nov. 2016 }
%	\end{etaremune}

\begin{samepage}	
\resheading{Service and Involvement}
	\begin{itemize}
		\item
			\ressubheading{High school tutor}{Apr. 2022 to Aug. 2022}{Northstar Tutors}{Washington, DC}
		\item
			\ressubheading{Chapter President}{Sep. 2019 to Sep. 2020}{UNL Graduate Chapter of the American Mathematical Society}{Lincoln, NE}
		\item 
			\ressubheading{Tutor for Native American high-school students}{Aug. 2019 to Mar. 2020}{Lincoln Public Schools}{Lincoln, NE}
		\item
			\ressubheading{Project mentor}{Aug. 2019 to May 2020}{UNL Math Dep. Directed Reading Program}{Lincoln, NE}
		\item
			\ressubheading{STAAR Seminar Co-organizer}{Aug. 2019 to Aug. 2020}{University of Nebraska-Lincoln Math Dept.}{Lincoln, NE}
		\item
			\ressubheading{Volunteer}{Jan. 2017 to Jan. 2020}{National Conference for Undergraduate Women in Mathematics}{Lincoln, NE}
		\item
			\ressubheading{Mentor to First-Year Graduate Students}{Aug. 2018 to May 2020}{University of Nebraska-Lincoln Math Dept.}{Lincoln, NE}
		\item
			\ressubheading{Representative to Graduate Student Advisory Board}{May 2016 to May 2018}{University of Nebraska-Lincoln Math Dept.}{Lincoln, NE}
		\item
			\ressubheading{UNL Math Day Volunteer}{Nov. 2015 to Dec. 2020}{University of Nebraska-Lincoln Math Dept.}{Lincoln, NE}
		
	\end{itemize}			
\end{samepage}
			
%\resheading{References and Contacts}
%
%\vspace{0.2cm}
%Available upon request.
\end{document}
